PM Mungbean meta-analysis

### 2021-05-25 02_Preliminary_analysis.Rmd
add severity rating table to compendium, and save for paper

>>>>

<br>  
<br>  
## Define powdery mildew severity
Powdery mildew severity was assessed on a 1 - 9 scale.
```{r disease_scale}
d_rating_table <-
   data.frame(
      Severity_rating = 1:9,
      Description = c(
         "No sign of powdery mildew",
         "Small colonies in the lower 1/3 of canopy with up to 75% of plants infected",
         "Colonies in lower half of canopy with more than 75% of plants infected",
         "Colonies in lower 2/3 of canopy with up to 75% of plants infected",
         "Colonies in lower 2/3 of canopy with more than 75% of plants infected",
         "Colonies in lower 2/3 of canopy with 100% of plants infected",
         "Colonies in lower 2/3 of canopy with 100% of plants infected, some plants with colonies in the top 1/3 of the canopy",
         "Colonies all the way to the top of the plant with more than 75% of plants affected",
         "Colonies all the way to the top of the plant with severe leaf drop"
      )
   ) %>%
   flextable() %>%
   autofit() %>%
   set_header_labels(Severity_rating = "Severity rating") %>%
   align(j = 1, align = "center")
d_rating_table
```
```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = d_rating_table)
print(doc, target = "paper/figures/SeverityTable.docx")
```
